Energy and the CES production function

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fix bug introduced when cleaning up code.

    # return this.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
      )
  }
  ) %>% bind_rows() %>%

  # Change variable names to make a nicer-looking graph and relevel factors before plotting
  mutate( variable = plyr::mapvalues(
    variable,
    from=c("iGDP", 
           "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
           "iL", "ihLest",
           "iXpMP", "iXp", "iUMP", "iU"),
    to=c("y", 
         "k", "k", "k", "k",
         "l", "l",
         "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")),
    flavor = ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted"))
  )

>>>>

    # return this.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      variable = as.character(variable), # eliminate factors, which cause warnings with bind_rows() below.
      Country = Country,
      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
      )
  }
  ) %>% bind_rows() %>%

  # Change variable names to make a nicer-looking graph and relevel factors before plotting
  mutate( variable = plyr::mapvalues(
    variable,
    from=c("iGDP", 
           "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
           "iL", "ihLest",
           "iXpMP", "iXp", "iUMP", "iU"),
    to=c("y", 
         "k", "k", "k", "k",
         "l", "l",
         "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")),
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted"))
  )
